---
title: "Snakebite-miRNA -- Novel miRNA module report"
output: pdf_document
date: "`r format(Sys.time(), '%d %B %Y, %H:%M')`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

if (!exists("project_folder")) {
  project_folder <- getwd()
  pipeline_folder <- getwd()
  features_file <- "config/features.yaml"
  sample_file <- "config/samples.tsv"
}

source(file.path(pipeline_folder, "workflow", "scripts", "R", "report_helpers.R"))
```

## Overview

This report covers the **novel_mirna** module: per-sample genome coverage (mpileup),
merging of covered loci across samples, and removal of already-annotated regions to
yield a set of candidate novel-miRNA loci.

## Predicted novel-miRNA loci

```{r novel-loci}
bed <- safe_read_tsv(file.path(project_folder, "results", "novel_mirna", "bedtools", "novelLoci.bed"), col_names = FALSE)
if (nrow(bed) > 0) {
  colnames(bed)[1:3] <- c("chrom", "start", "end")
  bed$width_bp <- bed$end - bed$start
}
preview_table(bed, n = nrow(bed), caption = "Candidate novel-miRNA loci")
```

`r if (nrow(bed) > 0) sprintf("**%d** candidate loci were predicted, with a median width of %.0f bp.", nrow(bed), stats::median(bed$width_bp)) else "No candidate loci have been predicted yet."`

```{r width-plot, fig.width=6, fig.height=3}
if (nrow(bed) > 0) {
  ggplot2::ggplot(bed, ggplot2::aes(x = width_bp)) +
    ggplot2::geom_histogram(bins = 30, fill = "#00B5E2") +
    ggplot2::labs(title = "Novel-miRNA locus width distribution", x = "Width (bp)", y = "Loci") +
    ggplot2::theme_minimal(base_size = 11)
}
```

## Runtime and resource usage

```{r runtime}
bench <- discover_benchmarks(project_folder, "novel_mirna")
runtime_table(bench, caption = "novel_mirna module: runtime and peak memory per rule")
resource_allocation_table(bench, "novel_mirna", project_folder,
                           caption = "novel_mirna module: allocated vs. actual resource usage")
```

```{r runtime-plot, fig.width=7, fig.height=3}
runtime_plot(bench, title = "novel_mirna module: total runtime per rule")
```
